Marine species do not need visas: the transboundary nature of the world’s exploited marine species

### 2020-08-04 Scripts/Manuscript_Draft.Rmd
updated values

Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete). For example, our study shows that Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile and thus discrete for Ecuador (**spatial threshold between Ecuador and Peru < 10%**) **[@Cashion:2018cg]**. The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 7.3 million tons representing USD 12,710 million in fishing revenue **over the same time period**. Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**. These species represented only **an annual average of** 2.8 million tons and 4,282 million USD between 2005 and 2014. These results underscore the importance of transboundary species at the global level.

We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average yearly** revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD). The estimated revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05) (Fig. 1B). China (USD 7,284 million) in **Eastern** Asia and the USA **in Northern America** (USD 11,604 million) contribute 55% and 82% to the **annual average** revenues. In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 **million**) and Japan (USD 3,907 **million**) are among the top five countries with the most fishing revenue generated from transboundary species in the last decade. These five nations are responsible for 41% of the global fisheries revenue from transboundary species.

>>>>

Based on our assessment (see Methods), 582 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete). For example, our study shows that Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile and thus discrete for Ecuador (**spatial threshold between Ecuador and Peru < 10%**) **[@Cashion:2018cg]**. The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 7.5 million tons representing USD 12,941 million in fishing revenue **over the same time period**. Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**. These species represented only **an annual average of** 2.8 million tons and 4,282 million USD between 2005 and 2014. These results underscore the importance of transboundary species at the global level.

We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average country** revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD). The estimated **per country** revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05) (Fig. 1B). China (USD 7,284 million) in **Eastern** Asia and the USA **in Northern America** (USD 11,604 million) contribute 55% and 82% to the **annual average** revenues. In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 **million**) and Japan (USD 3,907 **million**) are among the top five countries with the most fishing revenue generated from transboundary species in the last decade. These five nations are responsible for 41% of the global fisheries revenue from transboundary species.
